User–generated content is shifting towards momentary glimpses into people's lives. Sharing short–lived videos and live feeds has become an increasingly integral part of every day life.
Big online corporations like Facebook and Google profit from this growing demand and provide ad–supported platforms to share live content with large audiences.
However, smaller services struggle to keep up as they lack the means to provide the necessary infrastructure.

Decentralised applications (dApps) have emerged to democratise content distribution, computation and storage.
\gls{p2p} networks directly connect end–user devices without a commercially–owned server and without a single point of failure. Breakthroughs in distributed routing and mesh nets have proven their real–world viability.

With advances in browser capabilities and the wide–spread support for \gls{webrtc}, it has become possible to build a web application with \gls{p2p} technology – which has traditionally been reserved for specialised software.

We propose a novel approach for distributed media streaming in the browser. Our design provides algorithms for independent agents, that build a distributed overlay mesh network and construct a \gls{dag} of video stream connections. We implement a \gls{sdk} to allow a variety of use–cases. Our implementation is verified using custom simulation proceedings and aspects of scalability and resilience to failure are analysed. The proposed design strives to inspire the next generation of distributed media live streaming platforms.
